Chemically Self-Consistant Modeling of the Globular Cluster NGC 2808 and its Effects on the Inferred Helium abundance of Multiple Stellar Populations.

### 2023-07-21 src/sections/fidanka.tex
Started working on the fidanka testing section

\subsection{Fidanka Testing}
In order to validate fidanka we have run a series of tests on synthetic CMDs
generated from NGC 2808 isochrones. For each test we use fidanka to both build
a synthetic population and then measure the fiducial line of that population.
The measured fiducial lines(s) are then compared to the underlying isochrones
used.

>>>>

\subsection{Fidanka Testing}
In order to validate fidanka we have run an series of injection recovery tests
using \fidanka's population synthesis routines to build various synthetic
populations and \fidanka's fiducial measurement routines to recover these
populations. We run multiple tests in order to validate \fidanka's ability to
extract varying numbers of populations without the prior of the exact population
number. Table \ref{tab:fidankaTests} provides the parameters for each injection recovery
test along with the $\chi^{2}$ difference between each isochrone and its associated fiducial line.
